Ceph Parallel File System Evaluation Report

### 2013-08-19 ceph-eval.tex
Misc fixs
Update branch mgmt in readme; update figures 11, 12 with I/O and better
labels; clarify "client network max" and "writes (including journals)"
on those figures as well.

@@

Despite the excellent write throughput we saw during the individual server
tests, throughput did not scale.  We spent a significant amount of time
investigating this phenomenon. Ultimately, we were able to replicate this finding
when running concurrent disk throughput tests directly on the servers without
Ceph involved. The second RAID processor on each DDN controller would max out when
three or more LUNs were written concurrently. It turns out the root of the problem
was a regression on DDN firmware update -- in particular, the cache
mirroring was not behaving as it should.

@@

@@

In the single server case as shown in Figure~\ref{fig:rados-064-osd},
performance gets very close to the hardware limits at roughly 9 OSDs per server
and then mostly levels out.

We also repeated tests looking at RADOS Bench performance as the
number of OSD server nodes increases. The results are summarized in
Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
scales nearly linearly for both reads and writes.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=4in]{ior-kernel-39}
\caption{Kernel changes to 3.9, IOR with 4 MB transfer size}
\label{fig:ior-kernel-39}
\end{figure}

>>>>

%% FEIYI: 6, 7 all fixed.

@@

Despite the excellent write throughput we saw during the individual server
tests, throughput did not scale.  We spent a significant amount of time
investigating this phenomenon. Ultimately, we were able to replicate this finding
when running concurrent disk throughput tests directly on the servers without
Ceph involved. The second RAID processor on each DDN controller would max out when
three or more LUNs were written concurrently. It turns out the root of the problem
was a regression on DDN firmware update -- in particular, the cache
mirroring was not behaving as it should.\footnote{DDN recently released a new
firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
a chance to verify it during our test cycle.}

@@

%% FEIYI: add footnote to clarify the issue.

@@

In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
(including Journals)'' refers to how much data is actually being written out the
DDN chasis, and blue line is how much data the clients are writing.
We observe that performance gets very close to the hardware limits at roughly 9
OSDs per server and then mostly levels out.

We also repeated tests looking at RADOS Bench performance as the number of OSD
server nodes increases from one to four. The results are summarized in
Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
scales nearly linearly for both reads and writes.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=4in]{ior-kernel-39}
\caption{CephFS performance with Kernel changes to 3.9, IOR with 4 MB transfer
size}
\label{fig:ior-kernel-39}
\end{figure}
